Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-21 talk_ucl_cdt_200622/conclusion.tex
add outline for CDT talk on Monday

\begin{frame}
	\frametitle{The QASS Algorithm}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Application on Toy Theory}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

% TODO Graham: add some more slides here depending on your preferences

>>>>

\begin{frame}
	\frametitle{Conclusion}

	Decoupled approach:

	\begin{itemize}
		\item
			Tuned and compared surrogates from 9~state-of-the-art families.
		\item
			Found heuristic: GBTs for $<10^4$~points and
			ANNs for $\geq10^5$~points.
		\item
			Fastest found surrogate predicts TBR with standard deviation of
			error~$\num{0.033}$ in~\SI{0.898}{\micro\second}, which is~$8\cdot
			10^6\times$~faster than Paramak.
		\item
			While this used 500K~datapoints, we found surrogates with
			comparable properties with as little as 10K~datapoints.
	\end{itemize}

	\vspace{0.5em}

	Adaptive approach:
	\begin{itemize}
		\item 
			TODO % TODO Graham
		\item
			TODO % TODO Graham
		\item
			TODO % TODO Graham
		\item
			TODO % TODO Graham
	\end{itemize}

	\vspace{0.5em}

	Presented methods portable $\rightarrow$ can be used as cheap
	approximation of any simulation or black box function.
\end{frame}

### 2020-06-21 talk_ucl_cdt_200622/introduction.tex
use beamer block for problem description
add model list to outline slide
Call updates

@@

\begin{frame}
	\frametitle{Problem Description}
	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
	\begin{align*}
		\isotope[1][0]{n} + \isotope[6][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He}
		\qquad\qquad
		\isotope[1][0]{n} + \isotope[7][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He} + \isotope[1][0]{n}
	\end{align*}
	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline

@@

	\begin{center}
	    \textbf{Our Challenge:}
	\end{center}

	\begin{center}
	    \textbf{Produce a fast TBR function which strongly approximates Paramak, making use of the latest in surrogate modelling techniques.}
	\end{center}
\end{frame}

@@

>>>>

%TODO: make all more concise, bullet points

@@

\begin{frame}
	\frametitle{Problem Description}
	Breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
	\begin{align*}
		\isotope[1][0]{n} + \isotope[6][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He}
		\qquad\qquad
		\isotope[1][0]{n} + \isotope[7][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He} + \isotope[1][0]{n}
	\end{align*}
	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline

@@

	\begin{block}{Our Challenge:}
		\begin{center}
			Produce a fast TBR function that strongly approximates Paramak, making use of the latest in surrogate modelling techniques.
		\end{center}
	\end{block}
\end{frame}

@@

		\vspace{2em}

### 2020-06-21 talk_ucl_cdt_200622/ucl_tbr_talk.tex
set graphics path, include UKAEA logo on the title slide
add CDT logo to the title page
add a slide on experiment 4
use title slide at section beginning
use the isotope package to typeset nuclear reactions

\documentclass{beamer}
\usetheme{ucl}
\useoutertheme[small]{ucltitlebanner}
\setbeamercolor{banner}{bg=darkblue}

%%%%%% Some other settings that can make things look nicer
%%% Set a smaller indent for description environment
\setbeamersize{description width=2em}
%%% Remove nav symbols (and shift any logo down to corner)
\setbeamertemplate{navigation symbols}{\vspace{-2ex}}

\setbeamertemplate{slide counter}[frameonly]

\title[Surrogate Modelling of the Tritium Breeding Ratio]{Surrogate Modelling of the Tritium Breeding Ratio}
\author[Petr Mánek \and Graham Van Goffrier]{Petr Mánek \and Graham Van Goffrier}
\institute[UCL]{%
	Centre for Doctoral Training in Data Intensive Science \\ %
	University College London
}
\date{22nd June 2020}

@@

\begin{frame}
  \titlepage%
\end{frame}

\section{Introduction}
\input{introduction}

@@

\section{Conclusion}
\input{conclusion}

>>>>

\documentclass{beamer}

% Main theme configuration
\usetheme{ucl}
\useoutertheme[small]{ucltitlebanner}
\setbeamercolor{banner}{bg=darkblue}

% Packages and settings
\usepackage{siunitx}
\usepackage{isotope}
\usepackage{hyperref}
\graphicspath{{./fig_final_report/}{./fig_paper/}{./fig/}}

\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}

% Set a smaller indent for description environment
\setbeamersize{description width=2em}

% Remove nav symbols (and shift any logo down to corner)
\setbeamertemplate{navigation symbols}{\vspace{-2ex}}

% Title slide logos
\newlength{\titlegraphicheight}
\setlength{\titlegraphicheight}{0.15\paperheight}
\titlegraphic{%
	\includegraphics[height=\titlegraphicheight]{cdt_dis_logo}%
	\hspace{15pt}%
	\includegraphics[height=\titlegraphicheight]{ukaea_logo}%
}

% Use title slide at section beginning
\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

% Metadata
\title[Surrogate Modelling of the Tritium Breeding Ratio]{Surrogate Modelling of the Tritium Breeding Ratio}
\author[Petr Mánek \and Graham Van Goffrier]{Petr Mánek \and Graham Van Goffrier}
\institute[UCL]{%
	Centre for Doctoral Training in Data Intensive Science \\ %
	University College London
}
\date{22nd June 2020}

@@

% Title slide
\begin{frame}
  \titlepage%
\end{frame}

% Body of the presentation is organized in separate files
\input{introduction}

@@

\input{conclusion}

\begin{frame}
	\vspace{2em}

	{\centering
		\begin{beamercolorbox}[sep=8pt,center]{title}
			\usebeamerfont{title} Thank you for listening! \par%
		\end{beamercolorbox}
	}

	\vspace{2em}

	Petr Mánek \dotfill \email{petr.manek.19@ucl.ac.uk}

	Graham Van~Goffrier \dotfill \email{graham.vangoffrier.19@ucl.ac.uk}

	\vspace{2em}

	{\footnotesize
	Further reading:
	\begin{itemize}
		\item
			\href{https://github.com/ucl-tbr-group-project/documentation/raw/pinboards-submitted/elevator_pitch/elevator_pitch.pdf}{Single page abstract (available online)}.
		\item
			\href{https://github.com/ucl-tbr-group-project/documentation/raw/pinboards-submitted/paper/ucl_tbr_paper.pdf}{Journal article, currently in internal pre-submission review (available online):\\
			\textit{Fast Regression of the Tritium Breeding Ratio in Fusion
		Reactors}}.
		\item
			\href{https://github.com/ucl-tbr-group-project/documentation/raw/published/final_report/tbr_final_report.pdf}{Industry group project final report (available online)}.
		\item
			All models, plots, training data, source code and technical documentation.
			\url{https://github.com/ucl-tbr-group-project}
	\end{itemize}
	}

\end{frame}
